Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-11 journal paper/content/sim_details.tex
Added a sentence.
Revised the intro para.

In this section we move to the reputation choice variant. Recall that in this variant of the model, instead of making choices between firms based on the Bayesian expected reward, each agent chooses the firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. We focus on numerical investigation of this model instead of analytical characterizations of equilibrium strategies.

@@

\xhdr{MAB algorithms.} We consider the same three classes of bandit algorithms discussed in Section~\ref{sec:intro-model}, but take a representative algorithm from each class and look for qualitative differences between the different classes. We will utilize Thompson Sampling (\TS) from the ``adaptive-exploration" MAB algorithms, the dynamic $\eps$-greedy (\DEG)\footnote{Throughout, we fix $\eps = 0.05$. Our pilot experiments showed that different $\eps$ did not qualitatively change the results.} from the ``exploration-separating" algorithms, and the ``dynamic greedy" algorithm (\DG) as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.

>>>>

\asedit{In this section we present our numerical simulations. As discussed in the Introduction, we focus on the \ExptsModel, whereby each agent chooses the firm with a maximal reputation score, modeled as a sliding window average of its rewards. Given the volume of experimental results, we (only) present the typical / representative ones in the body of the paper; the full results can be found in Appendix~\ref{app:expts}.}

%In this section we move to the reputation choice variant. Recall that in this variant of the model, instead of making choices between firms based on the Bayesian expected reward, each agent chooses the firm with a maximal reputation score (breaking ties uniformly). The reputation score is simply a sliding window average: an average reward of the last $M$ agents that chose this firm. We focus on numerical investigation of this model instead of analytical characterizations of equilibrium strategies.

@@

\xhdr{MAB algorithms.} We consider the same three classes of bandit algorithms discussed in Section~\ref{sec:intro-model}, but take a representative algorithm from each class and look for qualitative differences between the different classes. \asedit{Our pilot experiments indicate that our findings do not change substantially if other representative algorithms are chosen.}

We will utilize Thompson Sampling (\TS) from the ``adaptive-exploration" MAB algorithms, the dynamic $\eps$-greedy (\DEG)\footnote{Throughout, we fix $\eps = 0.05$. Our pilot experiments showed that different $\eps$ did not qualitatively change the results.} from the ``exploration-separating" algorithms, and the ``dynamic greedy" algorithm (\DG) as in Section~\ref{sec:theory-prelims}. For ease of comparison, all three algorithms are parameterized with the same ``fake" Bayesian prior: namely, the mean reward of each arm is drawn independently from a $\Beta(1,1)$ distribution. Recall that Beta priors with 0-1 rewards form a conjugate family, which allows for simple posterior updates.
